Data preparation

### 2024-02-07 procesamiento/02-prod_prep-macro.Rmd
up

**Solt SWDIID**
```{r Solt}
load(file = here::here("input/data/original/swiid9_5/swiid9_5.rda"))
solt <- 
swiid_summary %>% dplyr::select(country,year,gini_disp,gini_mkt) %>% dplyr::filter(year %in% c(2016))
solt$ccode <- countrycode::countrycode(sourcevar = solt$country,origin = "country.name",destination = "iso3n")
solt$country <- NULL
solt_2017 <-  solt %>% filter(ccode %in% countries$ccode) %>% 
  select(ccode,gini_disp,gini_mkt)
```

@@

```{r save}
save(df2,file = here::here("input/data/proc/study1_country.RData"))
haven::write_dta(data = df2,path = here::here("input/data/proc/study1_country.dta"))
sjPlot::view_df(df2,file =here::here("input/data/proc/codebook-s1.html") )
```

>>>>

**Solt SWDIID**
```{r Solt}
load(file = here::here("input/data/original/swiid9_5/swiid9_5.rda"))
solt <- 
swiid_summary %>% dplyr::select(country,year,gini_disp,gini_mkt,abs_red,rel_red) %>% dplyr::filter(year %in% c(2016))
solt$ccode <- countrycode::countrycode(sourcevar = solt$country,origin = "country.name",destination = "iso3n")
solt$country <- NULL
solt_2017 <-  solt %>% filter(ccode %in% countries$ccode) %>% 
  dplyr::select(ccode,gini_disp,gini_mkt,abs_red,rel_red)
```

@@

```{r save}
save(df2,file = here::here("input/data/proc/study1_country.RData"))
# haven::write_dta(data = df2,path = here::here("input/data/proc/study1_country.dta"))
sjPlot::view_df(df2,file =here::here("input/data/proc/codebook-s1.html") )
```
